\documentclass[12pt,headinclude,headsepline]{article}
\usepackage{comment}
\usepackage[compact]{titlesec}
\usepackage[margin=0.9in,papersize={8.5in,11in}]{geometry}
\usepackage{times}
\usepackage{hyperref}
\usepackage{wrapfig}
%
% Some useful packages. Add as you see fit.
%
\usepackage{graphicx}
\graphicspath{{./figures/}}
\usepackage{subfigmat}
\usepackage{wrapfig}
\usepackage{color}
\usepackage[numbers]{natbib}

%% %
%% % Header and Footer
%% %
%% \usepackage{fancyhdr}
%% \pagestyle{fancy}
%% \lhead{Integrated Supersonic Aircraft Concepts for Low-Boom, Low-Noise, and Low-Weight}
%% \chead{}
%% \rhead{}
%% \lfoot{}
%% \rfoot{\thepage}
%% \cfoot{}
%% \renewcommand{\headrulewidth}{0.4pt}
%% \renewcommand{\footrulewidth}{0.4pt}

\bibliographystyle{unsrt}
\begin{document}

\noindent {\bf Graeme J. Kennedy (co-PI)} \\
Assistant Professor \\
School of Aerospace Engineering, Georgia Institute of Technology \\
270 Ferst Drive \\
Atlanta, GA, 30318 \\
Phone: 404-894-9811, graeme.kennedy@ae.gatech.edu \\

\noindent {\bf PROFESSIONAL CREDENTIALS} \\
University of Toronto, Aerospace Engineering, B.A.Sc., 2005 \\
University of Toronto Institute for Aerospace Studies, M.A.Sc., 2007 \\
University of Toronto Institute for Aerospace Studies, Ph.D., 2012 \\

\noindent {\bf ACADEMIC / PROFESSIONAL APPOINTMENTS} \\
2013--present, Assistant Professor, Georgia Institute of Technology \\
2012--2013, Postdoctoral Fellow, University of Michigan \\

\noindent {\bf AWARDS} \\
2012 Green Aviation Research and Development Network (GARDN) Student Award \\
2007-2010 NSERC Canadian Graduate Scholarship – Doctoral Level \\
2006-2007 NSERC Canadian Graduate Scholarship – Masters Level \\
2005-2006 Ontario Graduate Scholarship \\
2004 NSERC Undergraduate Research Student Award \\ 
2001-2002 Walter F. Scott Memorial Entrance Scholarship \\

\noindent {\bf SELECTED PUBLICATIONS}

% Get rid of the references title
\renewcommand{\section}[2]{}

\begin{thebibliography}{1}

\bibitem{Kennedy:2014:TACS2}
Graeme~J. Kennedy and Joaquim~R.R.A. Martins.
\newblock A parallel finite-element framework for large-scale gradient-based
  design optimization of high-performance structures.
\newblock {\em Finite Elements in Analysis and Design}, 87(0):56 -- 73, 2014.

\bibitem{Kennedy:2014:tacs-tripan2}
Graeme~J. Kennedy and Joaquim R. R.~A. Martins.
\newblock A parallel aerostructural optimization framework for aircraft design
  studies.
\newblock {\em Structural and Multidisciplinary Optimization}, 2014.
\newblock Accepted.

\bibitem{Kennedy:2014:Aviation2}
Graeme~J. Kennedy, Gaetan K.~W. Kenway, and Joaquim R. R.~A. Martins.
\newblock Towards gradient-based design optimization of flexible transport
  aircraft with flutter constraints.
\newblock In {\em Aviation 2014}, Atlanta, Georgia, 2014.

\bibitem{James:2014:aerostruct-topo2}
Kai~A. James, Graeme~J. Kennedy, and Joaquim~R.R.A. Martins.
\newblock Concurrent aerostructural topology optimization of a wing box.
\newblock {\em Computers \& Structures}, 134(0):1 -- 17, 2014.

\bibitem{Kenway:2014:SPAHFA2}
Gaetan K.~W. Kenway, Graeme~J. Kennedy, and Joaquim R. R.~A. Martins.
\newblock Scalable parallel approach for high-fidelity steady-state aeroelastic
  analysis and adjoint derivative computations.
\newblock {\em AIAA Journal}, 52:935--951, 2014.

\bibitem{Kennedy:2013:SDM2}
Graeme~J. Kennedy and Joaquim R. R.~A. Martins.
\newblock An adjoint-based derivative evaluation method for time-dependent
  aeroelastic optimization of flexible aircraft.
\newblock In {\em Proceedings of the 54th AIAA/ASME/ASCE/AHS/ASC Structures,
  Structural Dynamics, and Materials Conference}, Boston, {MA}, April 2013.

\bibitem{Kennedy:2012:SMO2}
Graeme~J. Kennedy and Joaquim R. R.~A. Martins.
\newblock A laminate parametrization technique for discrete ply-angle problems
  with manufacturing constraints.
\newblock {\em Structural and Multidisciplinary Optimization}, pages 1--15,
  2013.

\bibitem{Kennedy:2011:HBT2}
Graeme~J. Kennedy and Joaquim R. R.~A. Martins.
\newblock A homogenization-based theory for anisotropic beams with accurate
  through-section stress and strain prediction.
\newblock {\em International Journal of Solids and Structures}, 49(1):54 -- 72,
  2012.

\bibitem{Kennedy:2011:IJSS2}
Graeme~J. Kennedy, Jorn~S. Hansen, and Joaquim R. R.~A. Martins.
\newblock A {T}imoshenko beam theory with pressure corrections for layered
  orthotropic beams.
\newblock {\em International Journal of Solids and Structures}, 48(16-17):2373
  -- 2382, 2011.

\bibitem{Kennedy:2010:HAM2}
Graeme~J. Kennedy and Jorn~S. Hansen.
\newblock The hybrid-adjoint method: {A} semi-analytic gradient evaluation
  technique applied to composite cure cycle optimization.
\newblock {\em Optimization and Engineering}, 11:23--43, 2010.

\end{thebibliography}
\end{document}
