\noindent {\bf Juan J. Alonso} \\
Associate Professor \\
Department of Aeronautics \& Astronautics \\
496 Lomita Mall, Durand Building, Room 252 \\
Stanford, CA 94305 \\
Phone: (650) 723-9954, Fax: (650) 725-3377, jjalonso@stanford.edu \\

\noindent {\bf PROFESSIONAL CREDENTIALS } \\
Massachusetts Institute of Technology,  Aeronautics \& Astronautics,            B.S., 1991  \\
Princeton University,                   Mechanical \& Aerospace Engineering,    M.A., 1993  \\
Princeton University,                   Mechanical \& Aerospace Engineering,    Ph.D., 1997  \\

\noindent {\bf ACADEMIC / PROFESSIONAL APPOINTMENTS}  \\
2004-present, Stanford University, Associate Professor \\
2006-2008, NASA Headquarters, Director, NASA Fundamental Aeronautics Program  \\
1997-2004, Stanford University, Assistant Professor  \\
1996-98, McDonnell Douglas Corporation, Aerodynamic Designer  \\

\noindent {\bf AWARDS } \\
2013 Balhaus prize Ð Advisor for best doctoral thesis in Aeronautics \& Astronautics \\
2010 Altitude World Record, Class U, Unmanned Aerial Vehicles, Electric.  Advisor \\
2009 NASA Exceptional Public Service Medal\\
2006 F.W. Baldwin Award for best paper published in the Canadian Aero \& Space Journal\\
2004, 2006, 2008 AIAA Best Paper Award, Multi-Disciplinary Optimization Conferences\\
AIAA Stanford Chapter Professor of the Year (7-time recipient during the 1998-2013 period) \\
2003 Balhaus prize Ð Advisor for best doctoral thesis in Aeronautics \& Astronautics\\
1998-99 Stanford University Terman Fellow\\
1996 Ray Grimm Memorial Price in Computational Physics\\
1995-96 Princeton University Honorific Fellow\\
1992 Speed World Record, Human-Powered Vehicle Over Water.  Team member\\
1990 Admiral Luis de Florez Award in Mechanical Engineering Design\\

\noindent {\bf COMMITTEE/ADVISORY COUNCIL MEMBERSHIP } \\
2013-present, AIAA AVIATION Executive Steering Committee\\
2013-present, Associate Editor, Computers \& Fluids\\
2013-present, INRIA Evaluation Board Member\\
2012-present, AIAA Associate Fellow\\
2012-present, DLR Institut fŸr Lufttransportsysteme Advisory Board\\
2012-present, ICCT Technical Advisory Group member\\
2011-2012, FAA AdministratorÕs Management Advisory Council\\
2010-present, Secretary of TransportationÕs Future of Aviation Advisory Council\\
2009-present, CGNS (CFD General Notation System) Advisory Committee\\
2009-2010, ICAO/CAEP Independent Expert Group for Aircraft Fuel Burn Goals/Regulations\\
2007-2009, IMDEA (Mathematics), Scientific Advisory Committee Member\\
2007-present, Stanford PSAAP / PSAAP 2 Center Steering Committee\\
2006-present, FAA REDAC, Office of Energy and Environment  \\
2005-present, Center for Turbulence Research Steering Committee \\
2005-07, NASA Advisory Council (Aeronautics Committee)  \\
2006-08, VAATE Steering Committee\\
2006-08, Fixed-Wing Vehicle Council Member\\
2004-06, AIAA Multi-Disciplinary Optimization Technical Committee\\

\noindent {\bf RECENT SELECTED / RELEVANT PUBLICATIONS}

\begin{enumerate}

\item Hicken, J. E. and Alonso, J. J., ``PDE-Constrained Optimization with Error Estimation and Control,Ó Accepted for publication, Journal of Computational Physics, 2013.

\item Alonso, J. J., Bonnefoy, P. A., Bono, J., Fan, A., McConnachie, D., Tracey, B. D., Wolpert, D., Xie, D., ``Application of Game Theoretic Models to Evaluate Airline Equipage Dynamics of NextGen Technologies," 2013 Aviation Technology, Integration, and Operations conference, 10.2514/6.2013-4279

\item Shimoyama, K., Kawai, S., and Alonso, J. J., ``Dynamic Adaptive Sampling Based on Kriging Surrogate Models for Efficient Uncertainty Quantification," AIAA Paper 2013-1470, 54th AIAA/ASME/ASCE/AHS/ASC Structures, Structural Dynamics, and Materials Conference, 2013, 10.2514/6.2013-1470

\item Palacios, F., Alonso, J. J., Colonno, M., Hicken, J., Lukaczyk, T, ``Adjoint-based method for supersonic aircraft design using equivalent area distribution," AIAA Paper 2012-0269, 50th AIAA Aerospace Sciences Meeting including the New Horizons Forum and Aerospace Exposition, Nashville, TN, January 2012.

\item Palacios, F., Duraisamy, K., Alonso, J. J., Zuazua, E., ``Robust Grid Adaptation for Efficient Uncertainty Quantification," AIAA Journal Vol. 50, No. 7, July 2012.

\item Alonso, J. J. and Colonno, M., ``Multidisciplinary Optimization with Applications to Sonic Boom Minimization," Annual Reviews of Fluid Mechanics, vol. 44: 505-526, January 2012.

\item Tracey, B, Wolpert, D., Alonso, J. J., ``Using supervised learning to improve Monte Carlo integral estimation," AIAA Journal.

\item Choi, S., Potsdam, M., Lee, K., Iaccarino, G., and Alonso, J. J., ``Helicopter Rotor Design Using a Time-Spectral ROM and Adjoint-Based Method," AIAA Paper 2008-5810, 12th AIAA/ISSMO Multidisciplinary Analysis and Optimization Conference, Victoria, British Columbia, September, 2008.

\item Mader, C., Martins, J., Alonso, J. J., and van der Weide, E., ``ADjoint: An Approach for the Rapid Development of Discrete Adjoint Solvers," AIAA Journal, vol. 46, no. 4, pp. 863-873, April 2008.  Best paper award, AIAA Multidisciplinary Analysis and Optimization Conference, 2008.

\item Choi, S., Alonso, J. J., Kroo, I. M., and Wintzer, M., ``Multifidelity Design Optimization of Low-Boom Supersonic Jets," AIAA Journal, vol. 45, no. 1, pp. 106-118, January-February 2008.

\item Colonno, M., Reddy, S., and Alonso, J. J., ``Multi-Fidelity Trajectory Optimization with Response Surface Based Aerodynamic Performance Prediction," AIAA Paper 2008-0218, 46th Aerospace Sciences Meeting \& Exhibit, Reno, Nevada, January 2008.

\item J. R. R. A. Martins, J. J. Alonso, and J. J. Reuther. ``A Coupled-Adjoint Sensitivity Analysis Method for High-Fidelity Aero-Structural Design. Optimization and Engineering," 6(1):33Ð62, March 2005.  Best paper award, AIAA Multidisciplinary Analysis and Optimization Conference, 2004.

\item Reuther, J.J., Alonso, J.J., Jameson, A., Rimlinger, M.J., Saunders, D., ``Constrained Multipoint Aerodynamic Shape Optimization Using an Adjoint Formulation and Parallel Computers: Parts I and II," AIAA Journal of Aircraft, vol. 36, no. 1, pp. 51-74, January-February 1999.

\end{enumerate}
